\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-26 paper.tex
Update on Overleaf.

\author{Séverin Lemaignan$^{1}$, Yoan Sallami$^{2}$, Christopher Wallbridge$^{1}$, Aurélie Clodic$^{2}$ and Rachid Alami$^{2}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk},
	$^{2}$Authors are with CNRS LAAS,
        Toulouse, France
        {\tt\small firstname.surname@laas.fr}}%
}

@@

\uwds is a distributed and lightweight open-source
framework \footnote{\url{https://github.com/underworlds-robot/underworlds}} that
enables robot programmers to build and refine spatial and temporal
models of the environment surrounding a robot in real-time. \uwds makes it possible to share
these world models amongst the software components running on the robot.
Additionally, \uwds enables users to represent and manipulate
\emph{multiple alternatives} to the current, perceived world model in a distributed manner. For
instance, the world with some objects filtered out; the world `viewed' from the
perspective of another agent; a hypothetical world resulting from the simulated
application of a plan, etc.

>>>>

\author{Séverin Lemaignan$^{1}$, Yoan Sallami$^{2}$, Christopher Wallbridge$^{1}$, Aurélie Clodic$^{2}$ and Rachid Alami$^{2}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk},
	$^{2}$Authors are with LAAS-CNRS, Université de Toulouse, CNRS, Toulouse, France
        {\tt\small firstname.surname@laas.fr}}%
}

@@

\uwds is a distributed and lightweight open-source
framework\footnote{\url{https://github.com/underworlds-robot/underworlds}} that
enables robot programmers to build and refine spatial and temporal
models of the environment surrounding a robot in real-time. \uwds makes it possible to share
these world models amongst the software components running on the robot.
Additionally, \uwds enables users to represent and manipulate
\emph{multiple alternatives} to the current, perceived world model in a distributed manner. For
instance, the world with some objects filtered out; the world `viewed' from the
perspective of another agent; a hypothetical world resulting from the simulated
application of a plan, etc.
